%!TEX root = ../thesis.tex
\section{Conclusions}
% Based on https://www.scribbr.com/dissertation/write-conclusion/
In this work I developed a distributed system which automates simulation-based testing of \glspl{av}.
Therefore it presents a formalization of test cases and explains all relevant strategies to generate simulations, handle simulator instances, evaluate test criteria during simulation executions, distribute simulation executions over a cluster and implement the communication between the components of \drivebuild{} and clients.
Its evaluation works with students as users of \drivebuild{} and utilizes their implementations of test generators and \glspl{ai}.
It showed that \drivebuild{} is able to cope with all these various approaches.
Further \drivebuild{} provides all metrics that either the implementations require to operate or the evaluation requires to analyze them.
Since the number of available test generators and \glspl{ai} is low and the quality of some of them is not as good as expected the metrics to analyze them yielded not as much interesting information as they could.
So future evaluation should consider even more test generators and \glspl{ai} (\eg{} \gls{dave}~\cite{dave}).
The evaluation also illustrates that \drivebuild{} is able to distribute test executions among a cluster and handle simulations and \glspl{av} in parallel.
Further it reveals that the performance when running \glspl{simnode} in \glspl{vm} on a shared cluster is very bad.
Research on the causes that affect the performance issues requires much more test executions and dedicated hardware resources.
Based on the experience which the evaluation yields possible causes may be low reliability of the low level socket communication or the fact that the hardware is virtualized.\\
However, there are already seminar courses at the university of Passau which use \drivebuild{} to test \glspl{ai}.
Further there is an ongoing discussion with researchers at the \enquote{Université du Québec à Chicoutimi, Canada} about integrating their event stream processing into \drivebuild{} to implement runtime verification and real-time monitoring.
Also at the \gls{zhaw} there is a thesis about testing \glspl{av} which utilizes \drivebuild{}.
